Material Culture Networks in Tonto Basin

### 2022-12-28 manuscript.Rmd
Added additional references for women making pottery.

There is one other aspect to these relations that I believe played an important role. A central way people identify themselves is by gender. Gender roles, like identity, can also vary in complex ways, but for the purposes of this analysis I will use a simplified model. Women made pottery and men made projectile points. This was not always true of course, but this fits the available data for the Hohokam [@Crown1996-xb; @VanPool2010-im, p. 253]. An examination of the burial record for the RPMS study shows no obvious indication that women made pottery, only that both men and women were buried with pottery [@Loendorf1998-ln, Table 10.7]. On the other hand, projectile points were almost exclusively buried with males. This does not mean that a man could not move pots from one site to another or that a woman could not do the same with a projectile point, but, in general, differences in point and ceramic networks are most likely to indicate differences in gender networks.

>>>>

There is one other aspect to these relations that I believe played an important role. A central way people identify themselves is by gender. Gender roles, like identity, can also vary in complex ways, but for the purposes of this analysis I will use a simplified model. Women made pottery and men made projectile points. This was not always true of course, but this fits the available data and expectations for the Hohokam [@Crown1996-xb; @Harry2010-hj; @VanPool2010-im, p. 253; @Whittlesey2010-ox]. An examination of the ethnographic record for the O'odham people, recognized descendants of the Hohokam, provides additional references that women made pottery [@Bahr2011-or, p.4; @Castetter1935-pq, p. 5-6; @Chona1936-mg, p. 44; @Joseph1949-ga, p. 57]. An examination of the burial record for the RPMS study shows no obvious indication that women made pottery, only that both men and women were buried with pottery [@Loendorf1998-ln, Table 10.7]. On the other hand, projectile points were almost exclusively buried with males. This does not mean that a man could not move pots from one site to another or that a woman could not do the same with a projectile point, but, in general, differences in point and ceramic networks are most likely to indicate differences in gender networks.
